\documentclass[11pt]{vitae}

\definecolor{dustyblue}{rgb}{0.2156, 0.5686, 0.8392}
\definecolor{myorange}{rgb}{0.9411, 0.5490, 0.2588}
\definecolor{mypurple}{rgb}{0.7568, 0.4862, 0.8117}
\usepackage[ %
  pdfencoding = auto, %
  pdftitle={Curriculum Vitae},
  pdfauthor={Brandon L. Barker},
  colorlinks,
  urlcolor={dustyblue},
  linkcolor={myorange},
]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\rhead{\thepage}
\lhead{Curriculum Vitae---Brandon Barker}
\renewcommand{\headrulewidth}{0.4pt}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\begin{document}
\thispagestyle{empty}
{\LARGE\scshape Brandon Barker}

\parbox[t]{186pt}{%
Computational Division\\
Computational Physics and Methods\\
Center for Theoretical Astrophysics\\
Los Alamos National Laboratory\\
}
\hfill
\parbox[t]{220pt}{%##
\href{mailto:barker@lanl.gov}{\texttt{barker@lanl.gov}}\\
\href{astrobarker.github.io}{\texttt{astrobarker.github.io}}\\
\href{https://github.com/astrobarker}{\texttt{https://github.com/astrobarker}}\\
}

\vspace{4.0ex plus1ex minus0.5ex}

\sectionheader{Education}
\begin{chronlist}
\item[2019--2024] Michigan State University. Dual PhD, Astronomy and Astrophysics \& 
 Computational Mathematics, Science, and Engineering.

\item[2014--2019] The University of Tennessee, Knoxville.  BS,
  with honors in physics, secondary major in mathematics,
  minor in astronomy, \emph{magna cum laude}.

\end{chronlist}

\sectionheader{Appointments}
\begin{chronlist}
\item[2024--Present] Metropolis Postdoctoral Fellow, Los Alamos National Laboratory
\item[2022--2024] Graduate Research Assistant, Center for Nonlinear Studies, Los Alamos National Laboratory
\item[2019--2024] NSF Graduate Research Fellow
\item[2019--2024] PhD Candidate, Michigan State University
\end{chronlist}

\publicationheader{Refereed publications}

\begin{publist}

\item \href{https://ui.adsabs.harvard.edu/abs/2025arXiv250903003R/abstract}{``Kilonovae and Long-duration Gamma-ray Bursts.''} M. Risti\'c, \textbf{B. L. Barker}, et al. 2025, The Astrophysical Journal, Submitted.

\item \href{https://ui.adsabs.harvard.edu/abs/2025ApJS..277...65H/abstract}{`` Not-quite-transcendental Functions for Logarithmic Interpolation of Tabulated Data.''} P. Hammond, ..., \textbf{B. L. Barker}. 2025, The Astrophysical Journal Supplement Series, Volume 277, Issue 2, id.65, 8 pp.

\item \href{https://ui.adsabs.harvard.edu/abs/2025ApJ...982...81M/abstract}{``Let There Be Neutrons! Hadronic Photoproduction from a Large Flux of High-energy Photons.''} M. Mummpower et al. 2025. The Astrophysical Journal, Volume 982, Issue 2, id.81, 16 pp.

\item \href{https://ui.adsabs.harvard.edu/abs/2025ApJ...979..148L/abstract}{``Physics-driven Explosions of Stripped High-mass Stars: Synthetic Light Curves and Spectra of Stripped-envelope Supernovae with Broad Light Curves.''} J. Lu, \textbf{B. L. Barker}, et al. 2025. The Astrophysical Journal, Volume 979, Issue 2, id.148, 13 pp.

\item \href{https://ui.adsabs.harvard.edu/abs/2024arXiv241009146B/abstract}{``Phoebus: Performance Portable GRRMHD for Relativistic Astrophysics.''} \textbf{B. L. Barker} et al. 2024. Submitted to ApJS.

\item \href{https://joss.theoj.org/papers/10.21105/joss.06805}{``Singularity-EOS: Performance Portable Equations of State and Mixed Cell Closures.''} J. M. Miller, et al. 2024. Journal of Open Source Software, 9(103), 6805.

\item \href{https://doi.org/10.48550/arXiv.2211.05789}{``Inferring Type II-P Supernova Progenitor Masses from Plateau Luminosities.''} \textbf{B. L. Barker}, E. O'Connor, S. M. Couch. 2023. The Astrophysical Journal Letters, Volume 944, Issue 1, id.L2, 7 pp.

\item \href{https://doi.org/10.3847/1538-4357/ac77f3}{``Connecting the Light Curves of Type IIP Supernovae to the Properties of their Progenitors.''} \textbf{B. L. Barker}, C. E. Harris, M. Warren, E. O'Connor, S. M. Couch. 2022. The Astrophysical Journal, Volume 934, Issue 1, id.67, 19 pp.

\item \href{https://iopscience.iop.org/article/10.3847/1538-4365/abd700}{``\textsc{Thornado}-hydro: a discontinuous Galerkin method for supernova hydrodynamics with nuclear equations of state.''} D. Pochik, \textbf{B. L. Barker}, E. Endeve, et al. 2021. The Astrophysical Journal Supplement Series, Volume 253, Issue 1, id.21, 44 pp.

\item \href{https://doi.org/10.1088/1742-6596/1225/1/012014}{``\textsc{Thornado}-hydro: towards discontinuous galerkin methods for supernova hydrodynamics.''} E. Endeve, J. Buffaloe, S. Dunham, N. Roberts, K. Andrew, \textbf{B. L. Barker}, D. Pochik, J. Pulsinelli, A. Mezzacappa. 2019. Journal of Physics: Conference Series, Volume 1225, Issue 1, article id. 012014 (2019).

\end{publist}

\sectionheader{Open Source Software Development}
\begin{genericlist}
        \item \href{https://github.com/astrobarker/athelas}{\textsc{Athelas}} | Lead Developer | 
  High order radiation hydrodynamics for astrophysical transients
\item \href{https://github.com/lanl/phoebus}{\textsc{Phoebus}} | Core Developer | 
  Performance portable GRRMHD
\item \href{https://github.com/parthenon-hpc-lab/parthenon}{\textsc{Parthenon}} | Developer | 
  Performance portable block structured adaptive mesh refinement
\item \href{https://github.com/lanl/singularity-eos}{\textsc{Singularity-eos}} | Developer | 
  Performance portable equation of state routines
\item \href{https://github.com/endeve/thornado}{\textsc{Thornado}} | Prior Developer | 
  Performance portable equation of state routines
\item \href{https://github.com/astrobarker/sordine}{\textsc{Sordine}} | Developer | 
  Small radiation hydrodynamics verification suite
\item \href{https://github.com/astrobarker/mplcolors}{\textsc{mplcolors}} | Developer | 
  Command line tool for color exploration.
\end{genericlist}

\sectionheader{Awards}
\begin{chronlist}
\item[2024] \textbf{Metropolis Computational Physics Postdoctoral Fellowship}
\item[2023] \textbf{MPA-Kavli Summer Research Fellow}
\item[2019] \textbf{NSF Graduate Research Fellowship}
\item[2019] \textbf{Michigan State University Enrichment Fellowship}
\item[2019] \textbf{FORD Foundation Predoctoral Fellowship Honorable Mention}
%  \item[2019] \textbf{Outstanding Presentation Award, APS April}
\item[2019] \textbf{Chancellor's Undergraduate Researcher of the Year, UTK}
\item[2018] \textbf{Barry Goldwater Scholarship Honorable Mention}
\item[2018] \textbf{Society of Physics Students (SPS) National Organization Leadership Award}
\item[2018] \textbf{SPS Outstanding Undergraduate Research Award Honorable Mention}
\item[2018] \textbf{Chancellor’s Citation Award, UTK} for Extraordinary Academic Achievement
\item[2018] \textbf{Chancellor’s Citation Award, UTK} for Extraordinary Professional Promise
\item[2018] \textbf{James W. McConnell Award for Academic Excellence, UTK}, Department of Physics and Astronomy
%  \item[2018] \textbf{Office of Research and Engagement Silver Award, UTK
%          &  for the Exhibition of Undergraduate Research and Creative Achievement
%  \item[2018] \textbf{Arts and Sciences Award, UTK
%          &  for the Exhibition of Undergraduate Research and Creative Achievement
\item[2018] \textbf{Cooper D. Schmitt Memorial Scholarship}, UTK, Department of Mathematics for academic merit
\item[2018] \textbf{Katherine M. Frierson Memorial Scholarship}, UTK, outstanding academic achievement
  \item[2018] \textbf{Inducted into Sigma Pi Sigma Physics Honor Society}
  \item[2017] \textbf{Katherine M. Frierson Memorial Scholarship, UTK}
  \item[2017] \textbf{Dr. Glenn R. and Elise I. Young Scholarship}, UTK, Department of Mathematics for academic merit
%  \item[2017] \textbf{Cooper D. Schmitt Memorial Scholarship, UTK, Department of Mathematics for academic merit
  \item[2017] \textbf{Outstanding Undergraduate Researcher}, UTK, Department of Physics and Astronomy
%  \item[2016] \textbf{Robert W. Lide Citation, UTK
%          & Department of Physics and Astronomy for contributions to physics labs
\end{chronlist}

\sectionheader{Tehcnical skills}
\begin{genericlist}
\item[] Languages \& Programming Models
\begin{itemize}
  \item[] \texttt{C/C++}, Kokkos, FORTRAN, Python, Julia
\end{itemize}
\item[] Software \& Numerical Instruments
\begin{itemize}
 \item[] \textsc{Phoebus}, \textsc{Parthenon}, \textsc{Flash}, \textsc{Athena}, \textsc{Thornado}, \textsc{Flash}, \textsc{Snec}
\end{itemize}
\end{genericlist}

%\sectionheader{Grants}
%
%
%\begin{genericlist}
%\end{genericlist}
%
%\sectionheader{Teaching}
%
%\begin{genericlist}
%\item Undergraduate courses
%\item Graduate courses
% \begin{itemize}
% \end{itemize}
%\end{genericlist}


\sectionheader{Outreach}
\begin{genericlist}

\item ``Exploring the Lives and Deaths of Stars Through Poetry.'' Astronomy on Tap public talk, Lansing, MI.

\item ``Exploring the Lives and Deaths of Stars Through Poetry.'' Astronomy on Tap public talk, Albuquerque, NM.

\item Annoor Academy Science Club --- Coordinator. Created lesson plans and assisted with demonstrations for an after school program at Annoor Academy, an Islamic school in Knoxville.

\item LEGO Reobitics League, Inskip Elemetary --- Activity Leader. Volunteer with an after school LEGO rebotics club.

\item Saturday Science Club --- Organizer, Leader. Write and run science experiments with students at Pond Gap Elementary School, a Title I community school in Knoxville. Monthly for 5 years.

\end{genericlist}

\sectionheader{Professional Mentorship}
\begin{genericlist}
\item Michigan State University Stellar Mentorship Program --- Leader, Mentor.
\item Michigan State University Physics and Astronomy REU --- Grad Student Mentor.
\item Advanced Computational Research Experience for Undergraduates -- Grad Student Mentor.
\end{genericlist}

\sectionheader{Service}
\begin{genericlist}
\item Conference organization
  \begin{itemize}
    \item[] CENAM Conference \emph{Frontiers in Nuclear Astrophysics 2025}, Ohio University
  \end{itemize}
\item Graduate School
  \begin{itemize}
      \item[] \href{https://astro.natsci.msu.edu/personal-and-professional-support/stellar-mentorship-program.aspx}{Michigan State University Stellar Mentorship Program}
      \item Michigan State University Astronomy Seminar Committee
      \item Goldwater Scholars' Community council
  \end{itemize}
\item Undergraduate
  \begin{itemize}
    \item Undergraduate Research Students' Association Executive Board
    \item UTK Journal of Undergraduate Research (Pursuit) Research Editor for Sciences and Engineering
    \item Dean's Student Advisory Council
  \end{itemize}
\end{genericlist}


\publicationheader{Invited talks}
\begin{publist}

\item ``On the prospects for r-process nucleosynthesis in collapsars'' Harvard Institute for Theory and Computation Lunch Talks. October 2023.

\item ``\textsc{Phoebus}: PHifty One Ergs Blows Up Stars'' Virtual Astronomy Software Talks. October 2023.

\item ``\textsc{Phoebus}: PHifty One Ergs Blows Up Stars'' Numerical Relativity Community Cal. June 2023.

\item ``On the prospects for r-process nucleosynthesis in collapsars'' LANL Astrophysics Distinguished Seminar Series. April 2023.

\item ``High-order Magnetohydrodynamics Simulations of Core-Collapse Supernovae with Two-Moment Neutrino Transport using FLASH'' SIAM Conference on Computational Science and Engineering. March 2021.

\end{publist}

\publicationheader{Colloquia and Seminars}

\begin{publist}

\item ``A Biased Overview of Computational Astrophysics.'' Rutgers Transient Soriee. 2025.

\end{publist}

\publicationheader{Other talks}

\begin{publist}

  \item ``On the prospects for r-process nucleosynthesis in collapsars'' Frontiers in Nuclear Astrophysics. May 2023.
  \item ``On the prospects for r-process nucleosynthesis in collapsars'' 242nd Meeting of the American Astronomical Society. May 2023.
  \item ``On the prospects for r-process nucleosynthesis in collapsars'' APS April Meeting 2023. April 2023.
  \item ``Type IIP Supernova Light Curves From Neutrino-Driven Explosions: Correlations, Degeneracies, and Core Constraints'' SuperVirtual Supernova Conference. November 2021.
  \item ``Constraining the Core Structure of Core-Collapse Supernovae'' 236th Meeting of the American Astronomical Society. June 2020.
  \item ``Constraining the Core Structure of Core-Collapse Supernovae'' 235th Meeting of the American Astronomical Society. January 2020.
  \item ``Application of the Discontinuous Galerkin Method to Supernova Hydrodynamics in thornado'' SIAM South Eastern Atlantic Section Meeting. September 2019.
  \item ``Equation of State Dependence of the Observable Properties of Turbulence-aided Neutrino-driven Core-collapse Supernovae'' APS April Meeting 2019. April 2019.
  \item ``Equation of State Dependence of the Observable Properties of Turbulence-aided Neutrino-driven Core-collapse Supernovae'' Exhibition of Undergraduate Research and Creative Achievement. April 2019.
  \item ``Equation of State Dependence of the Observable Properties of Turbulence-aided Neutrino-driven Core-collapse Supernovae'' Undergraduate Research Symposium. April 2019.
  \item ``Equation of State Dependence of the Observable Properties of Turbulence-aided Neutrino-driven Core-collapse Supernovae'' Exhibition of Undergraduate Research and Creative Achievement. April 2019.
  \item ``Effects of Input Nuclear Physics on Core Collapse Supernova Simulations'' Fifth Joint Meeting of the Nuclear Physics Divisions of the APS and JPS. October 2018.
  \item ``Effects of Input Nuclear Physics on Core Collapse Supernova Simulations'' Mid-Michigan Symposium for Undergraduate Research Experiences. July 2018.
  \item ``Prospects for High Energy Follow-up Studies of Gravitational Wave Transients'' Exhibition of Undergraduate Research and Creative Achievement. April 2018.
  \item ``Prospects for High Energy Follow-up Studies of Gravitational Wave Transients'' Undergraduate Research Symposium. April 2018.
  \item ``High Energy Follow-up Study of Gravitational Wave Transients'' 231st Meeting of the American Astronomical Society. January 2018.
  \item ``Discontinuous Galerkin Methods in Nuclear Astrophysics Simulations'' Exhibition of Undergraduate Research and Creative Achievement. April 2017.
  \item ``Discontinuous Galerkin Methods in Nuclear Astrophysics Simulations'' Sigma Pi Sigma Quadrennial Physics Conference. November 2016.
  \item ``A Singular Value Decomposition of 15M$_{\odot}$ Progenitor CHIMERA Data'' Exhibition of Undergraduate Research and Creative Achievement. April 2016.
  \item ``A Singular Value Decomposition of 15M$_{\odot}$ Progenitor CHIMERA Data'' Undergraduate Research Symposium. April 2016.
  \item ``A Singular Value Decomposition of 15M$_{\odot}$ Progenitor CHIMERA Entropy Data'' Southeast Section of the American Physical Society Annual Meeting. November 2015.

\end{publist}

% \\ press
\sectionheader{Press}
\begin{genericlist}
\item[] \href{https://www.fox47news.com/neighborhoods/good-neighbors/a-passion-for-the-stars-and-beer-inspires-this-weeks-good-neighbors}{``A passion for the stars and beer inspires this week's Good Neighbors''} --- Michigan local news segment about Astronomy on Tap.
\item[] ``Ask A Scientist: How Big Is A Quasar'' --- SciComm article in UTK’s campus newspaper, co-authored with Scott Satinover. 
\item[] ``Bridging The Synapse: Blue Light'' --- Podcast episode with Anu Kumar and Madeline MacArthur, guest appearance discussing the physics of light.
\end{genericlist}

\sectionheader{Undergraduate Research}
\begin{genericlist}
\item[] Advanced Computational Research Experience for Students — Summer Undergraduate Research Fellow, East Lansing, MI. May 2018 – August 2018. Worked with Sean Couch and MacKenzie Warren on core-collapse supernova sensitivity to nuclear physics variations.
  
\item[] Istituto Nazionale di Fisica Nucleare (INFN) — Summer Undergraduate Research Fellow, Pisa, Italy. June 2017 – August 2017. Studied gravitational wave and gamma ray burst joint detection rates with Barbara Patricelli under the DOE-INFN Exchange Program.
  
\item[] Joint Institute for Computational Sciences, ORNL — Undergraduate Researcher, Knoxville, TN. August 2016 – Present. Developed algorithms for supernova hydrodynamics using discontinuous Galerkin methods with Eirik Endeve and Anthony Mezzacappa.
  
\item[] Joint Institute for Advanced Materials, ORNL — Research Assistant, Knoxville, TN. May 2016 – August 2016. Built a vacuum suitcase and helped commission an X-ray photoelectron spectrometer with Norman Mannella and Paolo Vilmercati.
\end{genericlist}

\sectionheader{Work Experience}
\begin{genericlist}
  \item Undergraduate Learning Assistant — Department of Physics and Astronomy, UTK. January 2018 – May 2019. Tutored students, assisted with in-class activities, and graded for an introductory astronomy course.
  
  \item Grader — Department of Mathematics, UTK. January 2018 – May 2018. Graded written and computer assignments for a numerical algorithms course.
  
  \item Tutor — Department of Physics and Astronomy, UTK. August 2016 – May 2019. Tutored students in introductory physics and astronomy.
  
  \item Laboratory Setup Assistant — Department of Physics and Astronomy, UTK. October 2014 – December 2018. Set up equipment for introductory physics labs, coordinated with graduate TAs on lab activities and logistics.
\end{genericlist}

\end{document}
