%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{}{Brandon Lynn Barker}{ % Your name
Site: \urlstyle{same}\url{astrobarker.github.io}  % Your website, LinkedIn profile or other web address
Email: \href{mailto:bbarker5@vols.utk.edu}{barker49@msu.edu}
Twitter: \href{https://www.twitter.com/astrobarker}{\texttt{@AstroBarker}}
Github: \href{https://github.com/astrobarker}{\texttt{@AstroBarker}}
 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.36\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education}

\subsection{Michigan State University}

\descript{Ph.D., Astronomy and Astrophysics}
\location{College of Natural Sciences\\
Exp. 2024 | East Lansing, MI}

\sectionspace % Some whitespace after the section

\descript{Dual Ph.D., Computational Mathematics, Science, and Engineering}
\location{College of Natural Sciences\\
Exp. 2024 | East Lansing, MI }

%------------------------------------------------
\sectionspace % Some whitespace after the section


\subsection{University of Tennessee}
\descript{B.S., Physics, with Honors}
\location{Secondary Major in Mathematics \\
Minor in Astronomy \\
\emph{Magna Cum Laude} \\
College of Arts and Sciences \\
May 2019 | Knoxville, TN  }


\sectionspace % Some whitespace after the section

%------------------------------------------------



%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Technical Skills}

\descript{Languages \& Programming Models}

\texttt{C/C++} \textbullet{} \FORTRAN \textbullet{} \Python \textbullet{} \Julia \textbullet{} \Kokkos \textbullet{} \texttt{MPI}

\sectionspace % Some whitespace after the section

\descript{Software \& Numerical Instruments}

\phoebus \textbullet{} \FLASH \textbullet{} \thornado \textbullet{} \texttt{SNEC}
%------------------------------------------------
\sectionspace % Some whitespace after the section


\section{Advisors}
\descript{Graduate Advisor}
Sean Couch \\
Michigan State University \\
Jonah Miller \\
Los Alamos National Laboratory
\descript{Undergraduate Advisors}
Anthony Mezzacappa and Eirik Endeve\\
The University of Tennessee, Knoxville

%------------------------------------------------
\section{Advisees}
\descript{Current}
Anita Agasaveeran, MSU

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.63\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

%\section{Research Interests}
%Nuclear Astrophysics, Core-Collapse Supernovae, Collapsars, Nucleosynthesis, High Performance Computing, High-Order Numerical Methods

\section{Appointments}
\begin{tabular}{rl}
  2022 - Present & Graduate Research Assistant, Center for Nonlinear Studies, LANL \\
  2019 - Present & NSF Graduate Research Fellow \\
  2019 - Present & PhD Candidate, Michigan State University \\
\end{tabular}

\section{Publications}
%Add a location/description for metrics
\begin{itemize}

        \item ``Inferring Type II-P Supernova Progenitor Masses from Plateau Luminosities .'' \textbf{B. L. Barker}, E. O'Connor, S. M. Couch. 2023. \href{https://doi.org/10.48550/arXiv.2211.05789}{Accepted to ApJL}.
        \item ``Connecting the Light Curves of Type IIP Supernovae to the Properties of their Progenitors.'' \textbf{B. L. Barker}, C. E. Harris, M. Warren, E. O'Connor, S. M. Couch. 2022. \href{https://doi.org/10.3847/1538-4357/ac77f3}{ApJ, 934, 67}.

  \item ``\thornado-hydro: a discontinuous Galerkin method for supernova hydrodynamics with nuclear equations of state.'' D. Pochik, \textbf{B. L. Barker}, E. Endeve, et al. 2021. ApJS, 253, \href{https://iopscience.iop.org/article/10.3847/1538-4365/abd700}{21}.

  \item ``\thornado-hydro: towards discontinuous galerkin methods for supernova hydrodynamics.'' E. Endeve, J. Buffaloe, S. Dunham, N. Roberts, K. Andrew, \textbf{B. L. Barker}, D. Pochik, J. Pulsinelli, A. Mezzacappa. 2019, \href{https://doi.org/10.1088/1742-6596/1225/1/012014}{Journal of Physics: Conference Series, \texttt{1225}, 012014}.
   
%   \item ``\thornado-hydro: Generalizing discontinuous galerkin methods for a nuclear equation of state for supernova hydrodynamics.'' \textbf{B.~Barker}, E.~Endeve, A.~Mezzacappa. 2019. Undergraduate Thesis.

\end{itemize}

\section{Recent Awards}
\begin{tabular}{rl}
  2023 & \textbf{MPA-Kavli Summer Research Fellow} \\
    & Kavli Summer Program In Astrophysics \\
  2019 & \textbf{NSF Graduate Research Fellowship} \\
  2019 & \textbf{Michigan State University Enrichment Fellowship} \\
  2019 & \textbf{FORD Foundation Fredoctoral Fellowship Honorable Mention} \\
  2019 & \textbf{Outstanding Presentation Award, APS April} \\
  2019 & \textbf{Chancellor's Undergraduate Researcher of the Year, UTK} \\
  2018 & \textbf{Barry Goldwater Scholarship Honorable Mention} \\
  2018 & \textbf{Society of Physics Students (SPS) National Organization Leadership Award} \\
  2018 & \textbf{SPS Outstanding Undergraduate Research Award Honorable Mention}\\
  2018 & \textbf{Chancellor’s Citation Award, UTK}\\ & for Extraordinary Academic Achievement \\
  2018 & \textbf{Chancellor’s Citation Award, UTK}\\ &  for Extraordinary Professional Promise \\
  2018 & \textbf{James W. McConnell Award for Academic Excellence, UTK} \\
          &  from the Department of Physics and Astronomy \\
%  2018 & \textbf{Office of Research and Engagement Silver Award, UTK}\\
%          &  for the Exhibition of Undergraduate Research and Creative Achievement \\
%  2018 & \textbf{Arts and Sciences Award, UTK}\\
%          &  for the Exhibition of Undergraduate Research and Creative Achievement \\
  2018 & \textbf{Cooper D. Schmitt Memorial Scholarship, UTK}\\
          & from the Department of Mathematics for academic merit \\
  2018 & \textbf{Katherine M. Frierson Memorial Scholarship, UTK}\\
          & for outstanding academic achievement \\
  2018 & \textbf{Inducted into Sigma Pi Sigma Physics Honor Society} \\
  2017 & \textbf{Katherine M. Frierson Memorial Scholarship, UTK} \\
  2017 & \textbf{Dr. Glenn R. and Elise I. Young Scholarship, UTK}\\
          & Department of Mathematics for academic merit \\
  2017 & \textbf{Cooper D. Schmitt Memorial Scholarship, UTK}\\
          & Department of Mathematics for academic merit \\
  2017 & \textbf{Outstanding Undergraduate Researcher, UTK}\\
          & Department of Physics and Astronomy \\
  2016 & \textbf{Robert W. Lide Citation, UTK}\\
          & Department of Physics and Astronomy for contributions to physics labs  \\
\end{tabular}

\sectionspace % Some whitespace after the section

%------------------------------------------------


\end{minipage} % The end of the right column
\clearpage

%------------------------------------------------
% Career Mentoring
%------------------------------------------------

\section{Career Mentoring}

\runsubsection{Michigan State University Physics and Astronomy REU}
\descript{| Grad Student Mentor}

\location{Summer 2020}
One on one mentor for an REU student. Provided general career advice, checked on their well-being, and ensured that their REU experience was positive.
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{\href{https://icer-acres.msu.edu/}{Advanced Computational Research Experience for Undergraduates}}
\descript{| Grad Student Mentor}

\location{Summer 2021}
One of two grad student mentors for the ACRES REU. Led professional development and programming workshops and provided one one one mentoring to students.
\sectionspace % Some whitespace after the section

%------------------------------------------------



%------------------------------------------------
% Outreach
%------------------------------------------------

\section{Outreach}

\runsubsection{Annoor Academy Science Club}
\descript{| Coordinator}

\location{August 2018 - December 2018}
Created lesson plans and assisted with demonstrations for an after school science club at Annoor Academy, a private Islamic school in Knoxville.
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{LEGO Robotics League, Inskip Elementary}
\descript{| Activity Leader}

\location{August 2018 - December 2018}
Assist with an after school LEGO robotics club at Inskip Elementary, a local community school.
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Saturday Science Club}
\descript{| Activity Leader}

\location{September 2014 - December 2019}
Pond Gap Elementary School, a Title I community school in Knoxville, is visited monthly on Saturdays, and volunteers conduct science experiments and demonstrations with grade-school students with lesson plans written by volunteers.
\sectionspace % Some whitespace after the section

%------------------------------------------------

%------------------------------------------------
% Leadership
%------------------------------------------------

\section{Academic Leadership and Service}

\protected\def\hrefvcZfr{\href{https://astro.natsci.msu.edu/personal-and-professional-support/stellar-mentorship-program/}}
\runsubsection{\hrefvcZfr{Stellar Mentorship Program}}
\descript{| Graduate Student Leader}
\location{2020}
Offer mentorship and career support for all MSU astronomers -- from beginning undergraduates to faculty. Mentees are paired by career level, matching undergraduates with early grad students,
early grad students with senior grad students, and so on. In addition to mentorship, we plan professional development workshops for members of the department.
\sectionspace % Some whitespace after the section

\runsubsection{MSU Astronomy Seminar Committee}
\descript{| Graduate Student Representative}

\location{August 2020 - May 2021}
Graduate student representative for the MSU astronomy seminar. Help ensure seminar is conducted in a way that is both beneficial to graduate students and speakers.
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{MSU Astronomy Prospective Student Visit}
\descript{| Graduate Student Organizer}

\location{Spring 2020, Spring 2021}
Lead organization of the astronomy prospective student visits.
\sectionspace % Some whitespace after the section

%------------------------------------------------

%------------------------------------------------

\runsubsection{Goldwater Scholars' Community Council}
\descript{| Member}
\location{2019 - 2020}
Organize programming and events for Goldwater Scholars. Help to foster a
community among Scholars.
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Dean's Student Advisory Council}
\descript{| Member}

\location{August 2018 - May 2019}
Representative for the Department of Physics and Astronomy. Advise Dean of the College of Arts and Sciences
on issues of student concern.
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{\href{http://www.ursautk.org}{Undergraduate Research Students' Association}}
\descript{| Executive Board Member}

\location{January 2018 - May 2019}
Organize an annual undergraduate research symposium and promote undergraduate research across campus.
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Physics Journal Club}
\descript{| Co-Founder}

\location{January 2017 - May 2019}
Weekly meetings with faculty advisor to discuss a paper in physics or astronomy.
\sectionspace % Some whitespace after the section

%------------------------------------------------
\protected\def\hrefvcZfr{\href{https://trace.tennessee.edu/pursuit/}}
\runsubsection{\hrefvcZfr{Pursuit - The Journal of Undergraduate Research}}
\descript{| Research Editor for the Sciences and Engineering}

\location{August 2016 - May 2019}
Pursuit is a university wide, cross-discipline undergradaute research journal at UTK. Delegate submissions to referees and communicate with authors. Led a team of reviewers.
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{\href{http://www.utksps.org}{Society of Physics Students}}
\descript{| Executive Officer}

\location{August 2014 - May 2019}
Host numerous public outreach activities at local schools and other areas. Organize panels, trips to conferences, and host an undergraduate conference roughly once every other academic year.
\sectionspace % Some whitespace after the section

%------------------------------------------------


%------------------------------------------------
% Invited Talks
%------------------------------------------------

\section{Invited Talks}

\noindent \runsubsection{Numerical Relativity Community Call}
\descript{Invited Speaker | June 2023}
\location{``\textsc{Phoebus}: PHifty One Ergs Blows Up Stars''}
\sectionspace

\noindent \runsubsection{LANL Astrophysics Distinguished Seminar Series 2023}
\descript{Invited Speaker | April 2023}
\location{``On the prospects for r-process nucleosynthesis in collapsars''}
\sectionspace

\noindent \runsubsection{SIAM Conference on Computational Science and Engineering (CSE21)}\\
\descript{Computational Methods in Explosive Nuclear Astrophysics Minisymposium | March 2021 - Virtual}
\location{``High-Order Magnetohydrodynamic Simulations of Core-Collapse Supernovae with Two-Moment Neutrino Transport using Flash''}
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Presentations
%------------------------------------------------

\section{Presentations}

\noindent \runsubsection{Frontiers in Nuclear Astrophysics}
\descript{Oral Presenter | May 2023}
\location{``On the prospects for r-process nucleosynthesis in collapsars''}
\sectionspace

\noindent \runsubsection{242nd Meeting of the American Astronomical Society}
\descript{Oral Presenter | May 2023}
\location{``On the prospects for r-process nucleosynthesis in collapsars''}
\sectionspace

\noindent \runsubsection{APS April Meeting 2023}
\descript{Oral Presenter | April 2023}
\location{``On the prospects for r-process nucleosynthesis in collapsars''}
\sectionspace

\noindent \runsubsection{SuperVirtual Supernova Conference}
\descript{Student Presenter | November 2021}
\location{``Type IIP Supernova Light Curves From Neutrino-Driven Explosions: Correlations, Degeneracies, and Core Constraints''}
\sectionspace

\noindent \runsubsection{236th Meeting of the American Astronomical Society}\\
\descript{Student Presenter | June 2020 - Virtual}
\location{``Constraining the Core Structure of Core-Collapse Supernovae''}
\sectionspace % Some whitespace after the section

\noindent \runsubsection{235th Meeting of the American Astronomical Society}\\
\descript{Student Presenter | January 2020 - Honolulu, HI}
\location{``Constraining the Core Structure of Core-Collapse Supernovae''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{SIAM South Eastern Atlantic Section Meeting}\\
\descript{Student Presenter | September 2019 - Knoxville, TN}
\location{``Application of the Discontinuous Galerkin Method to Supernova Hydrodynamics in thornado''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{APS April Meeting 2019}\\
\descript{Student Presenter | April 2019 - Denver, CO}
\location{``Equation of State Dependence of the Observable Properties of Turbulence-aided Neutrino-driven Core-collapse Supernovae''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{Exhibition of Undergraduate Research and Creative Achievement}\\
\descript{Student Presenter | April 2019 - Knoxville, TN}
\location{``Equation of State Dependence of the Observable Properties of Turbulence-aided Neutrino-driven Core-collapse Supernovae''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{Undergraduate Research Symposium}\\
\descript{Student Presenter | April 2019 - Knoxville, TN}
\location{``Equation of State Dependence of the Observable Properties of Turbulence-aided Neutrino-driven Core-collapse Supernovae''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{Exhibition of Undergraduate Research and Creative Achievement}\\
\descript{Student Presenter | April 2019 - Knoxville, TN}
\location{``Equation of State Dependence of the Observable Properties of Turbulence-aided Neutrino-driven Core-collapse Supernovae''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{Fifth Joint Meeting of the Nuclear Physics Divisions of the APS and JPS}\\
\descript{Student Presenter | October 2018 - Waikoloa, HI}
\location{``Effects of Input Nuclear Physics on Core Collapse Supernova Simulations''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{Mid-Michigan Symposium for Undergraduate Research Experiences}\\
\descript{Student Presenter | July 2018 - East Lansing, MI}
\location{``Effects of Input Nuclear Physics on Core Collapse Supernova Simulations''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{Exhibition of Undergraduate Research and Creative Achievement}\\
\descript{Student Presenter | April 2018 - Knoxville, TN}
\location{``Prospects for High Energy Follow-up Studies of Gravitational Wave Transients''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{Undergraduate Research Symposium}\\
\descript{Student Presenter | April 2018 - Knoxville, TN}
\location{``Prospects for High Energy Follow-up Studies of Gravitational Wave Transients''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{231st Meeting of the American Astronomical Society}\\
\descript{Student Presenter | January 2018 - National Harbor, MD}
\location{``High Energy Follow-up Study of Gravitational Wave Transients''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{Exhibition of Undergraduate Research and Creative Achievement}\\
\descript{Student Presenter | April 2017 - Knoxville, TN}
\location{``Discontinuous Galerkin Methods in Nuclear Astrophysics Simulations''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{Sigma Pi Sigma Quadrennial Physics Conference}\\
\descript{Student Presenter | November 2016 - San Francisco, CA}
\location{``Discontinuous Galerkin Methods in Nuclear Astrophysics Simulations''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{Exhibition of Undergraduate Research and Creative Achievement}\\
\descript{Student Presenter | April 2016 - Knoxville, TN}
\location{``A Singular Value Decomposition of 15M$_{\odot}$ Progenitor CHIMERA Data''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{Undergraduate Research Symposium}\\
\descript{Student Presenter | April 2016 - Knoxville, TN}
\location{``A Singular Value Decomposition of 15M$_{\odot}$ Progenitor CHIMERA Data''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\noindent \runsubsection{Southeast Section of the American Physical Society Annual Meeting}\\
\descript{Student Presenter | November 2015 - Mobile, AL}
\location{``A Singular Value Decomposition of 15M$_{\odot}$ Progenitor CHIMERA Entropy Data''}
\sectionspace % Some whitespace after the section

%------------------------------------------------

%------------------------------------------------
% Press
%------------------------------------------------
%\clearpage
\section{Press}

\runsubsection{\href{http://www.utdailybeacon.com/opinion/columns/ask-a-scientist-how-big-is-a-quasar-compared-to/article_8b29b472-24ba-11e9-b461-2fb7fef8eef6.html}{Ask A Scientist: How Big Is A Quasar}}
\descript{\textbf{Brandon Barker} and Scott Satinover}
Scicomm article in UTK's campus newpaper adressing a submitted question about the size of quasars as part of
Ask A Scientist's column.

\sectionspace % whitespace

\runsubsection{\href{https://medium.com/bridging-the-synapse/7-blue-light-f69d4dac1669}{\textit{Bridging The Synapse}: Blue Light}}
\descript{Anu Kumar and Madeline MacArthur, Guest: \textbf{Brandon Barker}}
Appeared in an episode of \textit{Bridging The Synapse} to discuss the physics of light.


%------------------------------------------------
% Research
%------------------------------------------------

\section{Undergraduate Research Experience}

\runsubsection{Advanced Computational Research Experience for Students}
\descript{| Summer Undergraduate Research Fellow}

\location{May 2018 - August 2018 | East Lansing, MI}
Worked with \textbf{Sean Couch} and \textbf{MacKenzie Warren}
exploring the sensitivity of core-collapse supernovae to variations in input nuclear physics.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Instituto Nazionale di Fisica Nucleare (INFN)}
\descript{| Summer Undergraduate Research Fellow}

\location{June 2017 – August 2017 | Pisa, Italy}
Received a competitive scholarship under the DOE-INFN Student Exchange Program to work with \textbf{Barbara Patricelli}. Investigated possible joint detection rates for gravitational wave signals from binary neutron star mergers and short gamma ray bursts.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Joint Institute for Computational Sciences, ORNL}
\descript{| Undergraduate Researcher}

\location{August 2016 – Present | Knoxville, TN}
Developed algorithms for supernova hydrodynamics utilizing discontinuous Galerkin methods with \textbf{Eirik Endeve} and \textbf{Anthony Mezzacappa}.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Joint Institute for Advanced Materials, ORNL}
\descript{| Research Assistant}

\location{May 2016 – August 2016 | Knoxville, TN}
Developed a vacuum suitcase for use in the lab, and helped commission an X-ray photoelectron spectrometer with \textbf{Norman Mannella} and \textbf{Paolo Vilmercati}.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Joint Institute for Computational Sciences, ORNL}
\descript{| Undergraduate Researcher}

\location{May 2015 – May 2016 | Knoxville, TN}
Studied the impact of turbulent flows on the evolution of the supernova explosion with \textbf{Anthony Mezzacappa} and \textbf{Eirik Endeve}.

\sectionspace % Some whitespace after the section

%------------------------------------------------


%------------------------------------------------
% Work Experience
%------------------------------------------------

\section{Work Experience}

\runsubsection{Department of Physics and Astronomy, UTK}
\descript{| Undergraduate LA}

\location{January 2018 - May 2019}
Tutored students in an introductory astronomy class, helped with in-class activities, and graded for the instructor.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Department of Mathematics, UTK}
\descript{| Grader}

\location{January 2018 - May 2018}
Graded written and computer assignments for a numerical algorithms class.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Department of Physics and Astronomy, UTK}
\descript{| Tutor}

\location{August 2016 - May 2019}
Tutored students in introductory physics and astronomy.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Department of Physics and Astronomy, UTK}
\descript{| Laboratory Setup Assistant}

\location{October 2014 - December 2018}
Worked under the Director of Undergraduate Laboratories. Oversaw the setup of all 100-200 level introductory Physics lab sections. Worked with graduate TA’s to coordinate setup, lesson plans, and makeup labs.

\sectionspace % Some whitespace after the section

%------------------------------------------------




%------------------------------------------------
% Societies
%------------------------------------------------

% \section{Societies}
%
% \begin{tabular}{rll}
% 2014 & top 12\%ile & Tau Beta Pi Engineering Honor Society\\
% 2014 & National & The Global Leadership and Education Forum (tGELF)\\
% 2012 & National & Golden Key International Honor Society\\
% 2012 & National & National Society of Collegiate Scholars\\
% \end{tabular}
%
% \sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
